%-------------------------
% Vidush Singhal Resume — Jasmine Tang style
%-------------------------
\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.75in]{geometry}
% LuaLaTeX font setup
\usepackage{fontspec}

% Keep the original Latin Modern look under LuaLaTeX
\setmainfont{Latin Modern Roman}

% IPA font only for pronunciation
\newfontfamily\ipafont[
  Ligatures=TeX,
  Scale=MatchLowercase
]{Doulos SIL}

\newcommand{\ipa}[1]{{\ipafont /#1/}}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{multicol}


%------------------------------------------------
% COLOR & SPACING SETUP
%------------------------------------------------
\definecolor{accentblue}{RGB}{48,87,150}
\definecolor{textgray}{RGB}{45,45,45}
\definecolor{rulegray}{gray}{0.8}
\definecolor{navyblue}{RGB}{0,31,107}
\definecolor{sapphireblue}{RGB}{15,82,186}
\definecolor{ultramarineblue}{HTML}{0437F2}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\setlist[itemize]{noitemsep,topsep=2pt,leftmargin=1em}
\renewcommand{\baselinestretch}{1.05}

\titleformat{\section}
  {\large\bfseries\color{black}}
  {}{0pt}{}[\vspace{-1pt}\color{rulegray}\titlerule\vspace{-6pt}]

%------------------------------------------------
\begin{document}
%------------------------------------------------

\begin{center}
  {\Huge\textbf{Vidush Singhal}}\\[3pt]
  {\small \ipa{ʋɪ.d̪ŭʂ ˈsɪŋ.ɡʱəl}}\\[6pt]
  West Lafayette, IN, USA (Full-time roles starting 2027) \\
  \href{mailto:singhav@purdue.edu}{\textcolor{ultramarineblue}{singhav@purdue.edu}} \,|\, 
  \href{https://vidsinghal.github.io}{\textcolor{ultramarineblue}{vidsinghal.github.io}} \,|\, 
  \href{https://github.com/vidsinghal}{\textcolor{ultramarineblue}{github.com/vidsinghal}} \,|\, 
  \href{https://linkedin.com/in/vidush-singhal}{\textcolor{ultramarineblue}{linkedin.com/in/vidush-singhal}}\\
\end{center}
\vspace{-15pt}

%------------------------------------------------
\section*{Summary}
Ph.D. student in Electrical and Computer Engineering at Purdue University specializing in compiler infrastructure, program analysis, and performance optimization. Experienced with LLVM/Clang, MLIR/Torch-MLIR, GPU compiler tooling, automatic parallelization, data layout optimization, and software verification.
%------------------------------------------------
\section*{Experience}

\textbf{Microsoft Research \textcolor{ultramarineblue}{\href{https://www.microsoft.com/en-us/research/group/research-software-engineering-rise/}{(RiSE)}}} \hfill Redmond, WA\\
\textit{Research Intern} \hfill May 2025 -- Aug 2025
\begin{itemize}
  \item Built \texttt{C2Pulse}, an LLVM/Clang-based transpiler for verifying memory correctness of annotated C programs.
  %\item Built a pipeline from C to Pulse, which is ther verified by FStar.
  \item Implemented a Clang-to-Clang source transformer (\textbf{\textasciitilde7K LOC of C++}) that emits Pulse code for F* verification.
  \item Built a C benchmark suite and verified C components of DPE (Dice Protection Environment) through C2Pulse.
\end{itemize}

\textbf{Lawrence Livermore National Laboratory \textcolor{ultramarineblue}{\href{https://www.llnl.gov/}{(LLNL)}}} \hfill Livermore, CA\\
\textit{Computing Scholar Intern} \hfill May 2024 -- Aug 2024
\begin{itemize}
  \item Engineered an LLVM Attributor pass to optimize byte layout within stack allocations for improved spatial locality.
  \item Implemented LLVM IR analyses and transformations to eliminate dead bytes and reorder frequently accessed bytes.
  \item Reduced XSBench runtime by \textbf{6\%} when running under the sanitizer.
\end{itemize}

\textbf{Nod.ai Labs \textcolor{ultramarineblue}{\href{https://www.amd.com/en/newsroom/press-releases/2023-10-10-amd-to-acquire-open-source-ai-software-expert-nod-.html}{(Acquired by AMD)}}} \hfill Santa Clara, CA\\
\textit{Machine Learning Compiler Engineering Intern} \hfill May 2022 -- Aug 2022
\begin{itemize}
  \item Implemented Torch-MLIR kernels and compiler support for multiple PyTorch operators.
  \item Improved the PyTorch-to-MLIR compilation flow by expanding operator coverage.
  \item Added support for the Facebook DLRM recommendation model in the PyTorch-to-MLIR pipeline.
  \item Investigated ILP solver improvements for the Alpa scheduling framework.
\end{itemize}

\textbf{Purdue University - \textcolor{ultramarineblue}{\href{https://engineering.purdue.edu/~milind/}{PLCL Group}}} \hfill West Lafayette, IN\\
\textit{Graduate Research Assistant} \hfill May 2021 -- Present
\begin{itemize}
	     \item \textbf{Gibbon Compiler}
	      \begin{itemize}
	       \item Optimized layouts of recursive datatypes to improve spatial locality.
	       \item Measured \textbf{speedups of 1.14x to 54x} over the best prior work.
	       \item Implemented an array-of-structs to structure-of-arrays-style transformation for packed algebraic datatypes.
	       %\item This transformation can help with accelerating AI workloads written in Haskell.
	       \item Enabled selective traversal with \textbf{1.1x to 12x speedups} and ongoing loopification/vectorization optimizations.
	       \end{itemize}
       \item \textbf{Orchard Compiler}
       \begin{itemize}
       \item Developed a compiler framework to automatically fuse and parallelize tree traversals.
	       \item Measured \textbf{1x to 5x speedups} over baseline tree traversals.
	       \end{itemize}
      \item \textbf{Cornucopia}
      \begin{itemize} 
      %\item A framework for generating a corpus of binaries for a source file by utilizing compiler optimizations.
	      \item Developed a fuzzing-based framework to generate optimized binary corpora using \texttt{llc} optimization flags.
	      \item \textbf{Discovered bugs} in LLVM compiler optimization passes.
	      \item \textbf{Uncovered decompilation failures} in angr, Ghidra, and related binary analysis tools.
	      \item Embedded ground-truth metadata in generated binaries to evaluate binary analysis tools.
	      \end{itemize}
	      \item \textbf{Copse Compiler}
	      \begin{itemize} 
	      \item Developed a framework for vectorized evaluation of fully homomorphic encryption (FHE) decision trees.
      %\item Developed a compiler framework to automatically fuse and parallelize tree traversals.
      \end{itemize}
\end{itemize}

\textbf{Senior Design Project - \textcolor{ultramarineblue}{\href{https://engineering.purdue.edu/SoC-Team}{SoCET Team}}} \hfill West Lafayette, IN\\
\textit{Undergraduate Research} \hfill Jul 2020 -- May 2021
\begin{itemize}
    \item Developed an LLVM-based compiler tool for proprietary RISC-V hardware.
    %\item The compiler’s objective was to optimize C programs for sparsity.
    \item Implemented multiple LLVM RISC-V backend Machine IR passes to identify sparse program regions.
    \item Annotated sparse regions so hardware could detect them at runtime and perform runtime checks.
    %\item The hardware performed dynamic checks at runtime when it sees an annotated region.
\end{itemize}

%------------------------------------------------
\section*{Education}
\textbf{Purdue University}, West Lafayette, IN\\
Ph.D. in Electrical \& Computer Engineering \hfill Expected May 2027\\
M.S. in Electrical \& Computer Engineering \hfill May 2023\\
B.S. in Computer Engineering \hfill May 2021\\
% Vidush: TODO put course numbers here
\textbf{Relevant Coursework:} Compiler Code Generation and Optimization, Compilers for GPUs, Programming Parallel Machines, Reasoning About Programs, Programming Languages, Formal Languages/Computability/Parallelization, Holistic Software Security

%------------------------------------------------
\section*{Publications}
\begin{itemize}[leftmargin=1em]
  \item Raghav Malik, \textbf{Vidush Singhal}, Benjamin Gottfried, Milind Kulkarni. “Vectorized Secure Evaluation of Decision Forests.” \href{https://dl.acm.org/doi/abs/10.1145/3453483.3454094}{\textcolor{ultramarineblue}{\textit{PLDI 2021.}}}
  \item \textbf{Vidush Singhal}, Akul Abhilash Pillai, Charitha Saumya, Milind Kulkarni, Aravind Machiry. “Cornucopia: A Framework for Feedback Guided Generation of Binaries.” \href{https://dl.acm.org/doi/abs/10.1145/3551349.3561152}{\textcolor{ultramarineblue}{\textit{ASE 2022.}}}
  \item \textbf{Vidush Singhal}, Chaitanya Koparkar, Joseph Zullo, Artem Pelenitsyn, Michael Vollmer, Mike Rainey, Milind Kulkarni. “Optimizing Layout of Recursive Datatypes with Marmoset.” \href{https://drops.dagstuhl.de/entities/document/10.4230/LIPIcs.ECOOP.2024.38}{\textcolor{ultramarineblue}{\textit{ECOOP 2024.}}}
  \item \textbf{Vidush Singhal}, Laith Sakka, Kirshanthan Sundararajah, Ryan Newton, Milind Kulkarni. “Orchard: Heterogeneous Parallelism and Fine-grained Fusion for Complex Tree Traversals.” \href{https://dl.acm.org/doi/full/10.1145/3652605}{\textcolor{ultramarineblue}{\textit{ACM TACO 2024.}}}
  \item Chaitanya S. Koparkar, \textbf{Vidush Singhal}, Aditya Gupta, Mike Rainey, Michael Vollmer, Artem Pelenitsyn, Sam Tobin-Hochstadt, Milind Kulkarni, Ryan R. Newton. “Garbage Collection for Mostly Serialized Heaps.” \href{https://dl.acm.org/doi/abs/10.1145/3652024.3665512}{\textcolor{ultramarineblue}{\textit{ISMM 2024.}}}
\end{itemize}
%------------------------------------------------
\section*{Skills}
\textbf{Languages:} C, C++, Haskell, Python, Java, Bash, CUDA, Assembly (ARM, x86), SystemVerilog\\
\textbf{Compilers \& Verification:} LLVM, Clang, MLIR/Torch-MLIR, GCC, Coq, Dafny, F*, Pulse\\
\textbf{Parallel, Systems \& ML:} OpenMP, MPI, Pthreads, OpenCilk, Intel TBB, gem5, AFL++, GDB, Linux, PyTorch, TensorFlow, NumPy

%------------------------------------------------
\section*{Awards, Grants \& Service}
\textbf{Dean’s List and Semester Honors}, Purdue University \hfill (2017 - 2020)\\
\textbf{LLVM Developers’ Meeting Travel Grant} \hfill 2024\\ 
\textbf{Research Service} - AEC/PC/Reviewer for PLDI, CGO, ICFP, PPoPP, POPL, SPLASH, C3PO, JOSS \hfill (2023–2026)\\
\textbf{Seminar Co-Coordinator}, \textcolor{ultramarineblue}{\href{https://purduepl.github.io/index.html}{Purdue Programming Languages and Systems Research Group}} \hfill(2025 - present)\\

\end{document}
